---
title: "Figure_2E"
output: html_document
---

# GGplot font

```{r}

# https://stackoverflow.com/questions/27689222/changing-fonts-for-graphs-in-r

library(extrafont)

font_import()
loadfonts()       #Register fonts for Windows bitmap output
fonts() 

```

# Retrieve the number of unique upregulated pY per kinase

```{r}

library(tidyverse)

# read in list of kinase conditions (WT vs. dead), sorted in terms of the number of upregulated pY identified by mass spectrometry

Y_kinase_sorted <- read.table('Y_kinase_sorted.txt',sep='\t')
Y_kinase_sorted <- Y_kinase_sorted[,1]

```

# Load in the interaction data for the Leutert pS/pT sites

```{r}

leutert_pSpT_inter <- read.csv('Leutert_S2_pSpT_interactions.csv')

# construct ggplot2 data frame (PDB+AF2+I3D)

pSpT_int_col1 <- rep('pST \n(native)',nrow(leutert_pSpT_inter))
pSpT_int_col2 <- rep('pST \n(native)',nrow(leutert_pSpT_inter))
pSpT_int_col3 <- leutert_pSpT_inter[,3]
pSpT_int_col4 <- leutert_pSpT_inter[,6]
pSpT_int_col5 <- leutert_pSpT_inter[,11]

pSpT_int_PDB_AF2 <- data.frame(pSpT_int_col1,pSpT_int_col2,pSpT_int_col3,pSpT_int_col4,pSpT_int_col5)
pSpT_int_PDB_AF2 <- pSpT_int_PDB_AF2[!duplicated(pSpT_int_PDB_AF2),]

# construct ggplot2 data frame (ECLAIR)

pSpT_int_col1 <- rep('pST \n(native)',nrow(leutert_pSpT_inter))
pSpT_int_col2 <- rep('pST \n(native)',nrow(leutert_pSpT_inter))
pSpT_int_col3 <- leutert_pSpT_inter[,3]
pSpT_int_col4 <- leutert_pSpT_inter[,6]
pSpT_int_col5 <- leutert_pSpT_inter[,10]

pSpT_int_ECLAIR <- data.frame(pSpT_int_col1,pSpT_int_col2,pSpT_int_col3,pSpT_int_col4,pSpT_int_col5)
pSpT_int_ECLAIR <- pSpT_int_ECLAIR[!duplicated(pSpT_int_ECLAIR),]

```

# Plot the number of PDB/I3D interfaces 

```{r}

# Iterate through the 'master' files for each kinase and then use this to retrieve interaction data per pY and per kinase 

library(viridis)
library(clusterProfiler)

PDB_interfaces_df_global <- NULL

for (i in 1:length(Y_kinase_sorted)) {
  
  print(i)
  
  Y_kinase <- Y_kinase_sorted[i]
  
  # retrieve the name of the kinase
  Y_kinase_tag <- rapply(strsplit(Y_kinase_sorted[i], split=' '), function(x) x[1])
  
  master_file_path <- paste('~/Documents/Work/HFSP_2022/master_files/',Y_kinase_tag,'_master.csv',sep='')
  master_file <- read_csv(master_file_path)
  master_file <- data.frame(master_file,stringsAsFactors = F)
  
  # protein accession
  accession <- master_file$proteins
  
  #psite position
  pos <- master_file$pos_tag
    
  Y_kinase_group <- rapply(strsplit(Y_kinase_tag,split='-'), function(x) x[1])
  Y_kinase_tag <- rapply(strsplit(Y_kinase_tag,split='-'), function(x) x[2])
  
  # PDB/I3D (uniprot IDs for each interactor per pY)
  
  PDB_interfaces <- master_file$I3D_interactors
  if(is.null(PDB_interfaces)) {PDB_interfaces <- master_file$I3D.interactors}
  PDB_int_list <- lapply(strsplit(PDB_interfaces,split='/'), function(x) x[x != 'na']) 
  
  # AF2 (uniprot IDs for each interactor per pY)
  
  AF2_interfaces <- master_file$AF2_interactors
  if(is.null(AF2_interfaces)) {AF2_interfaces <- master_file$AF2.interactors}
  AF2_int_list <- lapply(strsplit(AF2_interfaces,split='/'), function(x) x[x != 'na']) 
  AF2_int_list <- lapply(AF2_int_list, function(x) stringr::str_trim(x))
  
  # Convert the AF2-based interactors into UniProt accessions so that they ca be compared with the PDB/I3D interactors
  AF2_int_list <- lapply(AF2_int_list, function(x) bitr(c('CDC28',x),fromType="GENENAME", toType=c("UNIPROT"), OrgDb="org.Sc.sgd.db")[,2]) #ID conversion; most will map successfully (ignore warnings for small number of IDs that do not map)
  AF2_int_list <- lapply(AF2_int_list, function(x) x[x != 'P00546'])
  
  # Combine in such a way that the same interface is not counted twice
  PDB_AF2_list <- mapply(c,PDB_int_list,AF2_int_list)
  PDB_AF2_list <- lapply(PDB_AF2_list, function(x) stringr::str_trim(x))
  PDB_interfaces <- rapply(PDB_AF2_list,function(x) length(unique(x)))
  PDB_interfaces_df <- data.frame(rep(Y_kinase_tag,nrow(master_file)), Y_kinase_group, accession, pos, PDB_interfaces, stringsAsFactors = FALSE)
  colnames(PDB_interfaces_df) <- c('Kinase','Interfaces')
  
  # Check that the number of accessions is equal to the length of the interface vector
  if(length(accession) != length(PDB_interfaces)) {stop()}
  if(length(pos) != length(PDB_interfaces)) {stop()}
  
  PDB_interfaces_df_global <- rbind(PDB_interfaces_df_global, PDB_interfaces_df)
  
}

colnames(PDB_interfaces_df_global) <- c('Kinase','Group','Accession','Position','Interfaces')

# Remove duplicate phosphosites (within groups)

PDB_interfaces_df_global <- PDB_interfaces_df_global[!duplicated(PDB_interfaces_df_global[,c(2,3,4)]),]

# Incorporate interaction data for the pSpT sites

colnames(pSpT_int_PDB_AF2) <- colnames(PDB_interfaces_df_global)
PDB_interfaces_df_global <- rbind(PDB_interfaces_df_global, pSpT_int_PDB_AF2)

# Arrange the group names into the desired order

PDB_interfaces_df_global$Group <- factor(PDB_interfaces_df_global$Group, levels = c('pY','pYd','vSRC','pST \n(native)'))

## generate the ggplot

library(gghalves)

p <- ggplot(PDB_interfaces_df_global, aes(x=Group, y=Interfaces, fill = Group, colour=Group)) + geom_half_violin(color='black',lwd=0.50,width=1.0,scale='width') +  geom_half_point()
p <- p + scale_fill_manual(values = c(rgb(49/255,104/255,142/255,128/255),rgb(53/255,183/255,121/255,128/255), rgb(253/255,231/255,37/255,128/255), rgb(147/255,112/255,219/255,128/255))) + 
                             scale_colour_manual(values = c(rgb(49/255,104/255,142/255,128/255),rgb(53/255,183/255,121/255,128/255), rgb(253/255,231/255,37/255,128/255), rgb(147/255,112/255,219/255,128/255)))

# Font
p <- p+theme_bw() + theme(text=element_text(face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))+theme(legend.position="none")

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")))

p <- p + ylab("No. of structural interfaces (per pY)") + xlab("") + ggtitle('')
p <- p+theme(axis.text=element_text(size=11),axis.title.x=element_text(size=11,face="plain"),axis.title.y=element_text(size=11.0,face="plain"),plot.title=element_text(size=18,face='bold'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none", panel.border = element_blank()) # axis.line = element_blank(), )
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+ylim(c(0,8.0))
p <- p+geom_text(data=data.frame(), aes(x=c(1:4), y=rep(7.8,4)), label=c(table(PDB_interfaces_df_global[,2])),col=colors()[190], fontface='plain', size=3.25, inherit.aes = FALSE)
ggsave(file='Figure_2e_left.pdf', plot=p, width=3.25, height=4.75)

# Write out the data frame for this plot

df <- PDB_interfaces_df_global
df[,1] <- gsub('\n','',df[,1])
df[,2] <- gsub('\n','',df[,2])

write.table(df,file='Figure_2E_df_structural_interfaces.txt',row.names=F,quote=F)
write.table(df,file='Figure_2E_df_structural_interfaces.tsv',row.names=F,quote=F,sep='\t')
write.csv(df,file='Figure_2E_df_structural_interfaces.csv',row.names=F,quote=F)

```

# Plot the number of interfaces predicted by Interactome INSIDER (per pY). N.B. their prediction algorithm is called 'ECLAIR'.

```{r}

library(viridis)

# Iterate through the 'master' files for each kinase and then use this to retrieve interaction data per pY and per kinase 

ECLAIR_interfaces_df_global <- NULL

for (i in 1:length(Y_kinase_sorted)) {
  
  print(i)
  
  Y_kinase <- Y_kinase_sorted[i]
  
  # retrieve the name of the kinase
  Y_kinase_tag <- rapply(strsplit(Y_kinase_sorted[i], split=' '), function(x) x[1])
  
  master_file_path <- paste(Y_kinase_tag,'_master.csv',sep='')
  master_file <- read_csv(master_file_path)
  master_file <- data.frame(master_file,stringsAsFactors = F)
  
  accession <- master_file$proteins
  pos <- master_file$pos_tag
    
  Y_kinase_group <- rapply(strsplit(Y_kinase_tag,split='-'), function(x) x[1])
  Y_kinase_tag <- rapply(strsplit(Y_kinase_tag,split='-'), function(x) x[2])
  
  # retrieve the number of predicted interfaces per phosphosite (Y) i.e. the 'ECLAIR' interfaces
  ECLAIR_interfaces <- master_file$ECLAIR_int_no.
  if(is.null(ECLAIR_interfaces)) {ECLAIR_interfaces <- master_file$ECLAIR.interactions}
  
  # Check that the number of accessions is equal to the length of the interface vector
  if(length(accession) != length(ECLAIR_interfaces)) {stop()}
  if(length(pos) != length(ECLAIR_interfaces)) {stop()}
  
  ECLAIR_interfaces_df <- data.frame(rep(Y_kinase_tag,nrow(master_file)), rep(Y_kinase_group,nrow(master_file)), accession, pos, ECLAIR_interfaces, stringsAsFactors = FALSE)
  colnames(ECLAIR_interfaces_df) <- c('Kinase','Interfaces')
  
  ECLAIR_interfaces_df_global <- rbind(ECLAIR_interfaces_df_global, ECLAIR_interfaces_df)
  
}

colnames(ECLAIR_interfaces_df_global) <- c('Kinase','Group','Accession','Position','Interfaces')

# Remove duplicate phosphosites (within groups)

ECLAIR_interfaces_df_global <- ECLAIR_interfaces_df_global[!duplicated(ECLAIR_interfaces_df_global[,c(2,3,4)]),]

# Incorporate interaction data for the pSpT sites

colnames(pSpT_int_ECLAIR) <- colnames(ECLAIR_interfaces_df_global)
ECLAIR_interfaces_df_global <- rbind(ECLAIR_interfaces_df_global, pSpT_int_ECLAIR)

# Arrange the group names into the desired order

ECLAIR_interfaces_df_global$Group <- factor(ECLAIR_interfaces_df_global$Group, levels = c('pY','pYd','vSRC', 'pST \n(native)'))

## generate the ggplot

library(gghalves)

p <- ggplot(ECLAIR_interfaces_df_global, aes(x=Group, y=Interfaces, fill = Group, colour=Group)) + geom_half_violin(color='black',lwd=0.50,width=1.0,scale='width') +  geom_half_point()
p <- p + scale_fill_manual(values = c(rgb(49/255,104/255,142/255,128/255),rgb(53/255,183/255,121/255,128/255), rgb(253/255,231/255,37/255,128/255), rgb(147/255,112/255,219/255,128/255))) + 
                             scale_colour_manual(values = c(rgb(49/255,104/255,142/255,128/255),rgb(53/255,183/255,121/255,128/255), rgb(253/255,231/255,37/255,128/255), rgb(147/255,112/255,219/255,128/255)))

# Font
p <- p+theme_bw() + theme(text=element_text(face="plain", size=15), panel.border = element_rect(color="black", size=1.2, linetype="solid"))+theme(legend.position="none")

# Ticks
p <- p+theme(axis.ticks.length=unit(-0.10, "cm"), axis.text.x = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")), axis.text.y = element_text(margin=unit(c(0.2,0.2,0.2,0.2), "cm")))

p <- p + ylab("No. of predicted interfaces (per pY)") + xlab("") + ggtitle('')
p <- p+theme(axis.text=element_text(size=11),axis.title.x=element_text(size=11,face="plain"),axis.title.y=element_text(size=11.0,face="plain"),plot.title=element_text(size=18,face='bold'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p + theme(legend.position = "none", panel.border = element_blank()) # axis.line = element_blank(), )
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+geom_text(data=data.frame(), aes(x=c(1:4), y=rep(202,4)), label=c(table(PDB_interfaces_df_global[,2])),col=colors()[190], fontface='plain', size=3.25, inherit.aes = FALSE)
ggsave(file='Figure_2e_right.pdf', plot=p, width=3.25, height=4.75)

# Write out the data frame for this plot

df <- ECLAIR_interfaces_df_global
df[,1] <- gsub('\n','',df[,1])
df[,2] <- gsub('\n','',df[,2])

write.table(df,file='Figure_2E_df_predicted_interfaces.txt',row.names=F,quote=F)
write.table(df,file='Figure_2E_df_predicted_interfaces.tsv',row.names=F,quote=F,sep='\t')
write.csv(df,file='Figure_2E_df_predicted_interfaces.csv',row.names=F,quote=F)

```

# Try to represent the data as a pie chart instead

```{r}

PDB_interfaces_df_global

# pY (group together sites with more than 2 interfaces)

pY_int_tab <- PDB_interfaces_df_global[PDB_interfaces_df_global[,2] == 'pY',]
pY_int_percs <- table(pY_int_tab[,5])/sum(table(pY_int_tab[,5]))*100
pY_int_percs_sup_2 <- sum(pY_int_percs[which(names(pY_int_percs) > 2)]) 
pY_int_percs <- c(pY_int_percs[which(names(pY_int_percs) <= 2)],pY_int_percs_sup_2)  
names(pY_int_percs)[length(pY_int_percs)] <- '2+'  

# pYd (group together sites with more than 2 interfaces)

pYd_int_tab <- PDB_interfaces_df_global[PDB_interfaces_df_global[,2] == 'pYd',]
pYd_int_percs <- table(pYd_int_tab[,5])/sum(table(pYd_int_tab[,5]))*100
pYd_int_percs_sup_2 <- sum(pYd_int_percs[which(names(pYd_int_percs) > 2)]) 
pYd_int_percs <- c(pYd_int_percs[which(names(pYd_int_percs) <= 2)],pYd_int_percs_sup_2)  
names(pYd_int_percs)[length(pYd_int_percs)] <- '2+' 

# vSRC (group together sites with more than 2 interfaces)

vSRC_int_tab <- PDB_interfaces_df_global[PDB_interfaces_df_global[,2] == 'vSRC',]
vSRC_int_percs <- table(vSRC_int_tab[,5])/sum(table(vSRC_int_tab[,5]))*100
vSRC_int_percs_sup_2 <- sum(vSRC_int_percs[which(names(vSRC_int_percs) > 2)]) 
vSRC_int_percs <- c(vSRC_int_percs[which(names(vSRC_int_percs) <= 2)],vSRC_int_percs_sup_2)  
names(vSRC_int_percs)[length(vSRC_int_percs)] <- '2+' 

# pST (group together sites with more than 2 interfaces)

pST_int_tab <- PDB_interfaces_df_global[PDB_interfaces_df_global[,2] == 'pST \n(native)',]
pST_int_percs <- table(pST_int_tab[,5])/sum(table(pST_int_tab[,5]))*100
pST_int_percs_sup_2 <- sum(pST_int_percs[which(as.numeric(names(pST_int_percs)) > 2)]) 
pST_int_percs <- c(pST_int_percs[which(as.numeric(names(pST_int_percs)) <= 2)],pST_int_percs_sup_2)  
names(pST_int_percs)[length(pST_int_percs)] <- '2+'

```

# Generate a stacked barplot with this data

```{r}

# pY

col1 <- rep('pY',4)
col2 <- c('0','1','2','2+')
col3 <- pY_int_percs
pY_stack_df <- data.frame(col1,col2,col3)
colnames(pY_stack_df) <- c('class','PPIs','perc')

# pYd

col1 <- rep('pYd',4)
col2 <- c('0','1','2','2+')
col3 <- pYd_int_percs
pYd_stack_df <- data.frame(col1,col2,col3)
colnames(pYd_stack_df) <- c('class','PPIs','perc')

# vSRC

col1 <- rep('vSRC',4)
col2 <- c('0','1','2','2+')
col3 <- vSRC_int_percs
vSRC_stack_df <- data.frame(col1,col2,col3)
colnames(vSRC_stack_df) <- c('class','PPIs','perc')

# pST

col1 <- rep('pST \n(native)',4)
col2 <- c('0','1','2','2+')
col3 <- pST_int_percs
pST_stack_df <- data.frame(col1,col2,col3)
colnames(pST_stack_df) <- c('class','PPIs','perc')

# combine

phospho_stack_df <- rbind(pY_stack_df,pYd_stack_df,vSRC_stack_df,pST_stack_df)
phospho_stack_df$PPIs <- factor(phospho_stack_df$PPIs, levels = rev(c('0','1','2', '2+')))
phospho_stack_df$class <- factor(phospho_stack_df$class, levels = c('pY','pYd','vSRC', 'pST \n(native)'))

p <- ggplot(phospho_stack_df, aes(alpha=PPIs, y=perc, x=class, fill=class)) + geom_bar(position="fill", stat="identity", width=0.7,size=0.5)
p <- p+scale_alpha_manual(values=c(0.025,0.2,0.4,0.85))
p <- p+scale_fill_manual(values=c(rgb(49/255,104/255,142/255),rgb(53/255,183/255,121/255), rgb(253/255,231/255,37/255), rgb(147/255,112/255,219/255)))
p <- p+theme_bw()
p <- p+scale_y_continuous(labels = scales::percent_format())
p <- p + theme(panel.border = element_blank())
p <- p+xlab('')+ylab('')+ggtitle('Structural interfaces')
p <- p+theme(plot.title=element_text(size=12.5,face='plain'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p+guides(fill = FALSE)
p <- p + guides(alpha=guide_legend(title="PPIs"))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA, NA)))
ggsave(file='Figure_2e_stacked_left.pdf', plot=p, width=3.75, height=4.5)

# write to file

write.table(phospho_stack_df,file='Figure_2E_left_stacked.txt',row.names=F,quote=F)
write.table(phospho_stack_df,file='Figure_2E_left_stacked.tsv',row.names=F,quote=F,sep='\t')
write.csv(phospho_stack_df,file='Figure_2E_left_stacked.csv',row.names=F,quote=F)

```

# As before but this time for the predicted interfaces

```{r}

ECLAIR_interfaces_df_global

# pY (group together sites with more than 2 interfaces)

pY_int_tab <- ECLAIR_interfaces_df_global[ECLAIR_interfaces_df_global[,2] == 'pY',]
pY_int_percs <- table(pY_int_tab[,5])/sum(table(pY_int_tab[,5]))*100
pY_int_percs_sup_2 <- sum(pY_int_percs[which(as.numeric(names(pY_int_percs)) > 2)]) 
pY_int_percs <- c(pY_int_percs[which(as.numeric(names(pY_int_percs)) <= 2)],pY_int_percs_sup_2)  
names(pY_int_percs)[length(pY_int_percs)] <- '2+'  

# pYd (group together sites with more than 2 interfaces)

pYd_int_tab <- ECLAIR_interfaces_df_global[ECLAIR_interfaces_df_global[,2] == 'pYd',]
pYd_int_percs <- table(pYd_int_tab[,5])/sum(table(pYd_int_tab[,5]))*100
pYd_int_percs_sup_2 <- sum(pYd_int_percs[which(as.numeric(names(pYd_int_percs)) > 2)]) 
pYd_int_percs <- c(pYd_int_percs[which(as.numeric(names(pYd_int_percs)) <= 2)],pYd_int_percs_sup_2)   
names(pYd_int_percs)[length(pYd_int_percs)] <- '2+' 

# vSRC (group together sites with more than 2 interfaces)

vSRC_int_tab <- ECLAIR_interfaces_df_global[ECLAIR_interfaces_df_global[,2] == 'vSRC',]
vSRC_int_percs <- table(vSRC_int_tab[,5])/sum(table(vSRC_int_tab[,5]))*100
vSRC_int_percs_sup_2 <- sum(vSRC_int_percs[which(as.numeric(names(vSRC_int_percs)) > 2)]) 
vSRC_int_percs <- c(vSRC_int_percs[which(as.numeric(names(vSRC_int_percs)) <= 2)],vSRC_int_percs_sup_2) 
names(vSRC_int_percs)[length(vSRC_int_percs)] <- '2+' 

# pST (group together sites with more than 2 interfaces)

pST_int_tab <- ECLAIR_interfaces_df_global[ECLAIR_interfaces_df_global[,2] == 'pST \n(native)',]
pST_int_percs <- table(pST_int_tab[,5])/sum(table(pST_int_tab[,5]))*100
pST_int_percs_sup_2 <- sum(pST_int_percs[which(as.numeric(names(pST_int_percs)) > 2)]) 
pST_int_percs <- c(pST_int_percs[which(as.numeric(names(pST_int_percs)) <= 2)],pST_int_percs_sup_2)  
names(pST_int_percs)[length(pST_int_percs)] <- '2+'

```

# Generate a stacked barplot with this data

```{r}

# pY

col1 <- rep('pY',4)
col2 <- c('0','1','2','2+')
col3 <- pY_int_percs
pY_stack_df <- data.frame(col1,col2,col3)
colnames(pY_stack_df) <- c('class','PPIs','perc')

# pYd

col1 <- rep('pYd',4)
col2 <- c('0','1','2','2+')
col3 <- pYd_int_percs
pYd_stack_df <- data.frame(col1,col2,col3)
colnames(pYd_stack_df) <- c('class','PPIs','perc')

# vSRC

col1 <- rep('vSRC',4)
col2 <- c('0','1','2','2+')
col3 <- vSRC_int_percs
vSRC_stack_df <- data.frame(col1,col2,col3)
colnames(vSRC_stack_df) <- c('class','PPIs','perc')

# pST

col1 <- rep('pST \n(native)',4)
col2 <- c('0','1','2','2+')
col3 <- pST_int_percs
pST_stack_df <- data.frame(col1,col2,col3)
colnames(pST_stack_df) <- c('class','PPIs','perc')

# combine

phospho_stack_df <- rbind(pY_stack_df,pYd_stack_df,vSRC_stack_df,pST_stack_df)
phospho_stack_df$PPIs <- factor(phospho_stack_df$PPIs, levels = rev(c('0','1','2', '2+')))
phospho_stack_df$class <- factor(phospho_stack_df$class, levels = c('pY','pYd','vSRC', 'pST \n(native)'))

p <- ggplot(phospho_stack_df, aes(alpha=PPIs, y=perc, x=class, fill=class)) + geom_bar(position="fill", stat="identity", width=0.7,size=0.5)
p <- p+scale_alpha_manual(values=c(0.025,0.2,0.4,0.85))
p <- p+scale_fill_manual(values=c(rgb(49/255,104/255,142/255),rgb(53/255,183/255,121/255), rgb(253/255,231/255,37/255), rgb(147/255,112/255,219/255)))
p <- p+theme_bw()
p <- p+scale_y_continuous(labels = scales::percent_format())
p <- p + theme(panel.border = element_blank())
p <- p+xlab('')+ylab('')+ggtitle('Predicted interfaces')
p <- p+theme(plot.title=element_text(size=12.5,face='plain'))
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p+guides(fill = FALSE)
p <- p + guides(alpha=guide_legend(title="PPIs"))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA, NA)))
ggsave(file='Figure_2e_stacked_right.pdf', plot=p, width=3.75, height=4.5)

# write to file

write.table(phospho_stack_df,file='Figure_2E_right_stacked.txt',row.names=F,quote=F)
write.table(phospho_stack_df,file='Figure_2E_right_stacked.tsv',row.names=F,quote=F,sep='\t')
write.csv(phospho_stack_df,file='Figure_2E_right_stacked.csv',row.names=F,quote=F)

```

