---
title: "Figure_S10a-b"
author: "David Bradley"
date: '2023-08-17'
output: html_document
---

```{r}

setwd("~/Documents/Work/HFSP_pelican/pelican_results_analysis")
pel_tab <- read.table('data/all_sites_pY_parameters_mss.txt', head=T)

# Exclude potential native pY sites and any spurious pY site that aligns to a human pY site 

pel_tab_acc_pos <- paste(pel_tab[,1],pel_tab[,4],sep='_')

## native sites

native_sites <- read.table('native_all_Lanz_Leutert_union.txt')
native_sites <- native_sites[,1]

## spurious pY that align to human pY

sc_py_hs_py_aligned <- read.csv('sc_pY_human_pY_aligned_4F.csv')
sc_py_hs_py_aligned_sites <- paste(sc_py_hs_py_aligned[,1],sc_py_hs_py_aligned[,3],sep='_')

# sites to exclude (native and human-aligning)

exclude_sites <- unique(c(native_sites,sc_py_hs_py_aligned_sites))

pel_tab <- pel_tab[!pel_tab_acc_pos %in% exclude_sites,]

```

# Number of significant sites for each category (bar plot - facet wrap FDR < 0.05 and FDR < 0.01)

```{r}

pt_all <- pel_tab[,c(2,11,12)]
colnames(pt_all) <- c('RSA','pvalue','class')
pt_all <- data.frame(pt_all,0)
pt_all[pt_all[,1] < 0.2,4] <- 'buried'
pt_all[pt_all[,1] > 0.4,4] <- 'exposed'
pt_all[pt_all[,1] >= 0.2 & pt_all[,1] <= 0.4,4] <- 'intermediate'

all_class_freq <- table(paste(pt_all[,3],pt_all[,4]))

### 0.05

    # Relative frequency of significant sites for each category
    
    pt_signif <- pt_all[pt_all[,2] < 0.05,]
    signif_class_freq <- table(paste(pt_signif[,3],pt_signif[,4]))
    signif_class_frac <- signif_class_freq / all_class_freq
    
    # construct the data frame
    
    col1 <- c('non_pY','pY','non_pY','pY','non_pY','pY')
    col2 <- c('buried','buried','intermediate','intermediate','exposed','exposed')
    col3 <- unname(signif_class_frac[c(1,4,3,6,2,5)])
    sig_frac_df <- data.frame(col1,col2,col3)
    sig_frac_df <- sig_frac_df[,-3]
    colnames(sig_frac_df) <- c('phospho','buried','freq')
    sig_frac_df[,3] <- sig_frac_df[,3]*100
    sig_frac_df[,1] <- gsub('non_pY','non-pY',sig_frac_df[,1])
    
    sig_frac_df$buried <- factor(sig_frac_df$buried, levels = c('buried','intermediate','exposed'))
    
    sig_frac_df_005 <- sig_frac_df 
    
### 0.01    
    
    # Relative frequency of significant sites for each category
    
    pt_signif <- pt_all[pt_all[,2] < 0.01,]
    signif_class_freq <- table(paste(pt_signif[,3],pt_signif[,4]))
    signif_class_frac <- signif_class_freq / all_class_freq
    
    # construct the data frame
    
    col1 <- c('non_pY','pY','non_pY','pY','non_pY','pY')
    col2 <- c('buried','buried','intermediate','intermediate','exposed','exposed')
    col3 <- unname(signif_class_frac[c(1,4,3,6,2,5)])
    sig_frac_df <- data.frame(col1,col2,col3)
    sig_frac_df <- sig_frac_df[,-3]
    colnames(sig_frac_df) <- c('phospho','buried','freq')
    sig_frac_df[,3] <- sig_frac_df[,3]*100
    sig_frac_df[,1] <- gsub('non_pY','non-pY',sig_frac_df[,1])
    
    sig_frac_df$buried <- factor(sig_frac_df$buried, levels = c('buried','intermediate','exposed'))
    sig_frac_df_001 <- sig_frac_df 
    
### all
    
    sig_frac_df_005 <- data.frame(sig_frac_df_005,'FDR < 0.05') 
    sig_frac_df_001 <- data.frame(sig_frac_df_001,'FDR < 0.01')
    colnames(sig_frac_df_005) <- c('phospho','buried','freq','threshold')
    colnames(sig_frac_df_001) <- c('phospho','buried','freq','threshold')
    sig_frac_df_all <- rbind(sig_frac_df_005, sig_frac_df_001)
    sig_frac_df_all$threshold <- factor(sig_frac_df_all$threshold, levels = c('FDR < 0.05','FDR < 0.01'))
    
### plot

### supplementary figure plot

p <- ggplot(sig_frac_df_all, aes(x=buried, y=freq, fill=phospho)) + geom_bar(stat="identity", position=position_dodge(), color='black', width=0.5)
p <- p + facet_wrap(vars(threshold))
p <- p+scale_fill_manual(values=c(colors()[220],'white'))
p <- p+theme_bw()
p <- p+xlab('')+ylab(expression('% significant'))
p <- p + theme(panel.border= element_blank())
p <- p+theme(axis.text=element_text(size=10),axis.title.x=element_text(size=10.2,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p+theme(strip.background = element_rect(fill = 'white'))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))

ggsave(file='Figure_S10a.pdf', plot=p, width=6.2, height=3.8)

```

# Pelican parameter analysis after removing non-pY with low maximum MSS, and with a Pelican p-value adjusted at an FDR of < 0.05

```{r}

# 5th percentile of pY mss scores

pY_nonpY_mss <- pel_tab[,c(12,13)] 
b <- pY_nonpY_mss[pY_nonpY_mss[,1] == 'pY',2]
fif_perc <- quantile(b,seq(0,1,0.01),na.rm=T)[6] # We use as our threshold of poor-quality target sites as those below the 5th percentile of maximum MSS across all tested kinases.

########

pt_all <- pel_tab[,c(2,9,11,12,13)]
colnames(pt_all) <- c('RSA','param','signif','class')
pt_all <- data.frame(pt_all,0)
pt_all[pt_all[,1] < 0.2,6] <- 'buried'
pt_all[pt_all[,1] > 0.4,6] <- 'exposed'
pt_all[pt_all[,1] >= 0.2 & pt_all[,1] <= 0.4,6] <- 'intermediate'

### Filter for 0.05 significance (Pelican FDR-adjusted p-value)

pt_signif <- pt_all[pt_all[,3] < 0.05,]
colnames(pt_signif) <- c('RSA','param','signif','phospho','max mss','buried')

## Select only non-phosphorylated sites that are below the 5th percentile max mss for phosphorylated sites
## (i.e. remove all of those above the 5th percentile)

filter_dex <- which(pt_signif[,4] == 'non_pY' & pt_signif[,5] > fif_perc)
pt_signif <- pt_signif[-filter_dex,]

###

sample_sizes <- table(paste(pt_signif[,4],pt_signif[,6]))
sample_sizes <- sample_sizes[c(1,4,3,6,2,5)]

###

## We will use ggsignif to plot the significance values. However, ggsignif does not seem to work very well when the data is grouped.
## Therefore, far below I have constructed a df that allows me to implement ggsignif to calculate the p-values. Then, I will
# take these p-values and then manually add them to my distributions below.

pt_signif$buried <- factor(pt_signif$buried, levels = c('buried','intermediate','exposed'))

## supplementary figure 9b

p <- ggplot(pt_signif, aes(x=buried, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = 'black', lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c(colors()[220],'white'))
p <- p+xlab('')+ylab(expression(Y[fungi] - Y[metazoa] ~  (pi[Pelican])))
p <- p+theme(axis.text=element_text(size=11.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(y_position = c(1.08,1.08,1.08), xmin = c(0.8,1.8,2.8), 
              xmax = c(1.2,2.2,3.2), annotation = c("0.19","0.0048","0.32"),
              tip_length = 0.02,textsize=3.1)
p <- p + geom_text(data=data.frame(), aes(x=c(0.78,1.22,1.78,2.22,2.78,3.22), y=rep(1.23,6), label=sample_sizes), size=2.85, inherit.aes = F)

ggsave(file='Supplementary_figure_10b.pdf', plot=p, width=5.55, height=3.5)

### geom_signif significance

pt_signif <- pt_signif %>% mutate(x2 = interaction(phospho, buried))
p <- ggplot(pt_signif, aes(x=x2, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c(mycol[30],mycol[12]))
p <- p+xlab('')+ylab(expression(Y[fungi] - Y[metazoa] ~  (pi[Pelican])))
p <- p+theme(axis.text=element_text(size=11.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(comparisons = list(c('non_pY.buried','pY.buried'),
                                        c('non_pY.intermediate','pY.intermediate'),
                                        c('non_pY.exposed','pY.exposed')),test='ks.test',test.args=list(alternative = "two.sided"))

```

