---
title: "HFSP_Pelican_prep"
author: "David Bradley"
date: '2023-08-17'
output: html_document
---

# In the previous scripts we wrote code to compute counter-selection against the phosphorylated tyrosine residue.
# Here we will perform siilar analysis but instead we will calculate counter-selection against motif residues.
# For this evolutionary analysis, it is important consider not only the motif of the phosphorylating kinase
# but as many tyrosine kinases as possible because selection will be acting with respect to all of the kinases
# and not just the kinases that we test in our experiments.

# First step is to select all non-pY/pY that have D-3/E-3 and then retrieve the selection parameters.

```{r}

### load in the table

setwd("~/Documents/Work/HFSP_pelican/pelican_results_analysis")
pel_tab <- read.table('data/all_sites_pY_parameters_mss.txt', head=T)

####

# Exclude potential native pY sites and any spurious pY site that aligns to a human pY site 

pel_tab_acc_pos <- paste(pel_tab[,1],pel_tab[,4],sep='_')

## native sites

native_sites <- read.table('native_all_Lanz_Leutert_union.txt')
native_sites <- native_sites[,1]

## spurious pY that align to human pY

sc_py_hs_py_aligned <- read.csv('sc_pY_human_pY_aligned_4F.csv')
sc_py_hs_py_aligned_sites <- paste(sc_py_hs_py_aligned[,1],sc_py_hs_py_aligned[,3],sep='_')

# sites to exclude (native and human-aligning)

exclude_sites <- unique(c(native_sites,sc_py_hs_py_aligned_sites))

pel_tab <- pel_tab[!pel_tab_acc_pos %in% exclude_sites,]

###

# extract flanking residues of interest

pel_tab_flank <- pel_tab[,7]
Pn3 <- substr(pel_tab_flank,5,5)
EDn3_dex <- which(Pn3 %in% c('D','E'))

pel_tab_EDn3 <- pel_tab[EDn3_dex,]

# N.B: I am not calculating RSA separately for each motif residue separately but instead just using the RSA derived
### from the phosphoacceptor Y.

```

# Extract the Pelican parameters for each -3 D/E residue (where possible)

```{r}

pelican_results <- list.files('/home/david/Documents/Work/HFSP_pelican/pelican_results')

count = 0

missing_vec <- NULL

selec_df <- NULL

for (i in 1:nrow(pel_tab_EDn3)) {
  
  print(i)
  
  accession <- pel_tab_EDn3[i,1]
  pos <- pel_tab_EDn3[i,4]
  
  #E/D-3
  
  pos <- pos-3
  
  rsa <- pel_tab_EDn3[i,2]
  disorder <- pel_tab_EDn3[i,3]
  
  # Retrieve the Pelican results for this protein
  
  pel_res_dex <- which(pelican_results %in% accession)
  
  # Skip if we do not have any Pelican results for this protein
  
  if (length(pel_res_dex) == 0) {next}
  
  # Skip if we have results (apparently?) but no parameters).
  
  param_tab <- paste('/home/david/Documents/Work/HFSP_pelican/pelican_results_parameters/',accession,'_pelican_parameters.txt',sep='')
  
  if(length(param_tab) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  param_lines <- readLines(param_tab)
  
  if(length(param_lines) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  params <- read.table(param_tab, head=T)
  
  # Map the phosho position to the alignment position
  
  map_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/mapping_tables/',paste(accession,'_mapping.txt',sep=''),sep=''), head=T)
  
  al_pos <- map_tab[map_tab[,2] == pos,3]
  trim_pos <- map_tab[map_tab[,2] == pos,4]
  
  # If we cannot locate a mapped position, then this means that the position was gappy and trimmed out by trimAL
  
  if (length(trim_pos) == 0) {next}
  
  # Alignment numbering is Python-based and so we need to account for that
  
  pel_pos <- trim_pos-1 
  
  phos_params <- params[params[,2] == pel_pos,]
  phos_params_0 <- phos_params[which(phos_params[,7] == '0'),]
  phos_params_1 <- phos_params[which(phos_params[,7] == '1'),]
  
  # Compile parameters (simply sum frequencies from all relevant residues)
  
  phos_params_0_Y <- phos_params_0[,colnames(phos_params_0) %in% c('D','E')]
  phos_params_1_Y <- phos_params_1[,colnames(phos_params_1) %in% c('D','E')]  
  phos_params_0_Y <- sum(phos_params_0_Y)
  phos_params_1_Y <- sum(phos_params_1_Y)
  
  # aaqtr pvalue
  
  pval_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/pelican_results/',accession,'/',accession,'_results/','all_sites.tsv',sep=''), head=T)
  pval_tab <- pval_tab[pval_tab[,2] == pel_pos,]
  naa <-  pval_tab[,4]
  multi_pval <- pval_tab[,5]
  aaqtr_pval <- pval_tab[,6]    
  
  # pY or non-pY
  
  class <- pel_tab_EDn3[i,12]
  
  # Put it all together
  
  selec_vec <- c(accession,rsa,disorder,pos,al_pos,trim_pos,phos_params_0_Y,phos_params_1_Y,naa,multi_pval,aaqtr_pval, class)
  
  selec_df <- rbind(selec_df, selec_vec)
  
} 

colnames(selec_df) <- c('accession', 'RSA','disorder','pos','al_pos', 'trim_pos', '0_DE','1_DE', 'naa','multinomial_p','aaqtr_p', 'class')
rownames(selec_df) <- NULL

selec_df_EDn3 <- selec_df

```

# Do FDR/BH-adjustment on the p-values and export table

```{r}

bh_adjust <- p.adjust(as.numeric(selec_df_EDn3[,11]),method='BH') #FDR and BH are exactly the same
selec_df_EDn3 <- data.frame(selec_df_EDn3,bh_adjust)
selec_df_EDn3 <- selec_df_EDn3[c(1:11,13,12)]

colnames(selec_df_EDn3) <- c('accession','RSA','order','sequence','alignment','trimmed','fungi_pelican_DE','metazoa_pelican_DE','naa','multinomial_p','pelican_pvalue','pelican_padjust', 'class')

selec_df_EDn3 <- selec_df_EDn3[,-c(9,10)]

# Difference between metazoa and fungal parameters

diff_vec <- as.numeric(selec_df_EDn3[,7]) - as.numeric(selec_df_EDn3[,8])

selec_df_EDn3 <- data.frame(selec_df_EDn3[,1:8],diff_vec,selec_df_EDn3[,9:11])
colnames(selec_df_EDn3)[9] <- 'pelican_param_Y_fungi_Y_metazoa' 

```

# Violin plot (D/E-3, Pelican parameters, FDR < 0.05)

```{r}

pt_all <- selec_df_EDn3[,c(2,9,11,12)]
colnames(pt_all) <- c('RSA','param','signif','class')
pt_all <- data.frame(pt_all,0)
pt_all[pt_all[,1] < 0.2,5] <- 'buried'
pt_all[pt_all[,1] > 0.4,5] <- 'exposed'
pt_all[pt_all[,1] >= 0.2 & pt_all[,1] <= 0.4,5] <- 'intermediate'

### 0.05

pt_signif <- pt_all[pt_all[,3] < 0.05,]
colnames(pt_signif) <- c('RSA','param','signif','phospho','buried')

###

sample_sizes <- table(paste(pt_signif[,4],pt_signif[,5]))
sample_sizes <- sample_sizes[c(1,4,3,6,2,5)]

###

pt_signif$buried <- factor(pt_signif$buried, levels = c('buried','intermediate','exposed'))

####

median.quartile <- function(x){
  out <- quantile(x, probs = c(0.25,0.5,0.75))
  names(out) <- c("ymin","y","ymax")
  return(out) 
}

mycol <- viridis::rocket(30)

####

library(ggsignif)

p <- ggplot(pt_signif, aes(x=buried, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c(mycol[12],mycol[30]))
p <- p+xlab('')+ylab(expression(ED[fungi] - ED[metazoa] ~  (pi[Pelican])))+ggtitle('E/D-3')
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p+theme(axis.text=element_text(size=10.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=12.2,face="plain"),plot.title=element_text(size=12.5,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(y_position = c(1.08,1.08,1.08), xmin = c(0.8,1.8,2.8), 
              xmax = c(1.2,2.2,3.2), annotation = c("0.013","0.96","0.065"),
              tip_length = 0.02)
p <- p+theme(legend.position = 'none')
p <- p + geom_text(data=data.frame(), aes(x=c(0.78,1.22,1.78,2.22,2.78,3.22), y=rep(1.23,6), label=sample_sizes), size=2.85, inherit.aes = F)

ggsave(file='Supplementary_figure_10c_DE.pdf', plot=p, width=4.25, height=3.15)

### geom_signif significance

pt_signif <- pt_signif %>% mutate(x2 = interaction(phospho, buried))
p <- ggplot(pt_signif, aes(x=x2, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c(mycol[30],mycol[12]))
p <- p+xlab('')+ylab(expression(Y[fungi] - Y[metazoa] ~  (pi[Pelican])))
p <- p+theme(axis.text=element_text(size=11.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(comparisons = list(c('non_pY.buried','pY.buried'),
                                        c('non_pY.intermediate','pY.intermediate'),
                                        c('non_pY.exposed','pY.exposed')),test='ks.test',test.args=list(alternative = "two.sided"))

```

# As before but this time for motif position I/L/V-1

```{r}

pel_tab_flank <- pel_tab[,7]
Pn1 <- substr(pel_tab_flank,7,7)
ILVn1_dex <- which(Pn1 %in% c('I','L','V'))

pel_tab_ILVn1 <- pel_tab[ILVn1_dex,]

# N.B: I am not calculating RSA separately for each motif residue separately but instead just using the RSA derived
### from the phosphoacceptor Y.
```

# Extract the parameter values where possible

```{r}

pelican_results <- list.files('/home/david/Documents/Work/HFSP_pelican/pelican_results')

count = 0

missing_vec <- NULL

selec_df <- NULL

for (i in 1:nrow(pel_tab_ILVn1)) {
  
  print(i)
  
  accession <- pel_tab_ILVn1[i,1]
  pos <- pel_tab_ILVn1[i,4]
  
  #E/D-3
  
  pos <- pos-1
  
  rsa <- pel_tab_ILVn1[i,2]
  disorder <- pel_tab_ILVn1[i,3]
  
  # Retrieve the Pelican results for this protein
  
  pel_res_dex <- which(pelican_results %in% accession)
  
  # Skip if we do not have any Pelican results for this protein
  
  if (length(pel_res_dex) == 0) {next}
  
  # Skip if we have results (apparently?) but no parameters).
  
  param_tab <- paste('/home/david/Documents/Work/HFSP_pelican/pelican_results_parameters/',accession,'_pelican_parameters.txt',sep='')
  
  if(length(param_tab) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  param_lines <- readLines(param_tab)
  
  if(length(param_lines) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  params <- read.table(param_tab, head=T)
  
  # Map the phosho position to the alignment position
  
  map_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/mapping_tables/',paste(accession,'_mapping.txt',sep=''),sep=''), head=T)
  
  al_pos <- map_tab[map_tab[,2] == pos,3]
  trim_pos <- map_tab[map_tab[,2] == pos,4]
  
  # If we cannot locate a mapped position, then this means that the position was gappy and trimmed out by trimAL
  
  if (length(trim_pos) == 0) {next}
  
  # Alignment numbering is Python-based and so we need to account for that
  
  pel_pos <- trim_pos-1 
  
  phos_params <- params[params[,2] == pel_pos,]
  phos_params_0 <- phos_params[which(phos_params[,7] == '0'),]
  phos_params_1 <- phos_params[which(phos_params[,7] == '1'),]
  
  # Compile parameters (simply sum frequencies from all relevant residues)
  
  phos_params_0_Y <- phos_params_0[,colnames(phos_params_0) %in% c('I','L','V')]
  phos_params_1_Y <- phos_params_1[,colnames(phos_params_1) %in% c('I','L','V')]  
  phos_params_0_Y <- sum(phos_params_0_Y)
  phos_params_1_Y <- sum(phos_params_1_Y)
  
  # aaqtr pvalue
  
  pval_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/pelican_results/',accession,'/',accession,'_results/','all_sites.tsv',sep=''), head=T)
  pval_tab <- pval_tab[pval_tab[,2] == pel_pos,]
  naa <-  pval_tab[,4]
  multi_pval <- pval_tab[,5]
  aaqtr_pval <- pval_tab[,6]    
  
  # pY or non-pY
  
  class <- pel_tab_ILVn1[i,12]
  
  # Put it all together
  
  selec_vec <- c(accession,rsa,disorder,pos,al_pos,trim_pos,phos_params_0_Y,phos_params_1_Y,naa,multi_pval,aaqtr_pval, class)
  
  selec_df <- rbind(selec_df, selec_vec)
  
} 

colnames(selec_df) <- c('accession', 'RSA','disorder','pos','al_pos', 'trim_pos', '0_ILV','1_ILV', 'naa','multinomial_p','aaqtr_p', 'class')
rownames(selec_df) <- NULL

selec_df_ILVn1 <- selec_df

```

# Do FDR/BH-adjustment on the p-values and export table

```{r}

bh_adjust <- p.adjust(as.numeric(selec_df_ILVn1[,11]),method='BH') #FDR and BH are exactly the same
selec_df_ILVn1 <- data.frame(selec_df_ILVn1,bh_adjust)
selec_df_ILVn1 <- selec_df_ILVn1[c(1:11,13,12)]

colnames(selec_df_ILVn1) <- c('accession','RSA','order','sequence','alignment','trimmed','fungi_pelican_DE','metazoa_pelican_DE','naa','multinomial_p','pelican_pvalue','pelican_padjust', 'class')

selec_df_ILVn1 <- selec_df_ILVn1[,-c(9,10)]

# Difference between metazoa and fungal parameters

diff_vec <- as.numeric(selec_df_ILVn1[,7]) - as.numeric(selec_df_ILVn1[,8])

selec_df_EDn3 <- data.frame(selec_df_ILVn1[,1:8],diff_vec,selec_df_ILVn1[,9:11])
colnames(selec_df_ILVn1)[9] <- 'pelican_param_Y_fungi_Y_metazoa' 

#write.table(selec_df_ILVn1,file='all_sites_ILVn1_parameters.txt',quote=F,row.names=F)

```

# Violin plot (ILVn-1, Pelican parameters, FDR < 0.05)

```{r}

pt_all <- selec_df_EDn3[,c(2,9,11,12)]
colnames(pt_all) <- c('RSA','param','signif','class')
pt_all <- data.frame(pt_all,0)
pt_all[pt_all[,1] < 0.2,5] <- 'buried'
pt_all[pt_all[,1] > 0.4,5] <- 'exposed'
pt_all[pt_all[,1] >= 0.2 & pt_all[,1] <= 0.4,5] <- 'intermediate'

### 0.05

pt_signif <- pt_all[pt_all[,3] < 0.05,]
colnames(pt_signif) <- c('RSA','param','signif','phospho','buried')

###

sample_sizes <- table(paste(pt_signif[,4],pt_signif[,5]))
sample_sizes <- sample_sizes[c(1,4,3,6,2,5)]

###

## We will use ggsignif to plot the significance values. However, ggsignif does not seem to work very well when the data is grouped.
## Therefore, far below I have constructed a df that allows me to implement ggsignif to calculate the p-values. Then, I will
# take these p-values and then manually add them to my distributions below.

pt_signif$buried <- factor(pt_signif$buried, levels = c('buried','intermediate','exposed'))

####

median.quartile <- function(x){
  out <- quantile(x, probs = c(0.25,0.5,0.75))
  names(out) <- c("ymin","y","ymax")
  return(out) 
}

mycol <- viridis::rocket(30)

####

library(ggsignif)

p <- ggplot(pt_signif, aes(x=buried, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c('#00AA00','#D7F4D7'))
p <- p+xlab('')+ylab(expression(ED[fungi] - ED[metazoa] ~  (pi[Pelican])))+ggtitle('I/L/V-1')
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p+theme(axis.text=element_text(size=10.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=12.2,face="plain"),plot.title=element_text(size=12.5,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(y_position = c(1.08,1.08,1.08), xmin = c(0.8,1.8,2.8), 
              xmax = c(1.2,2.2,3.2), annotation = c("0.94","0.74","0.066"),
              tip_length = 0.02)
p <- p+theme(legend.position = 'none')
p <- p + geom_text(data=data.frame(), aes(x=c(0.78,1.22,1.78,2.22,2.78,3.22), y=rep(1.23,6), label=sample_sizes), size=2.85, inherit.aes = F)

ggsave(file='Supplementary_figure_10c_ILV.pdf', plot=p, width=4.25, height=3.15)

### geom_signif significance

pt_signif <- pt_signif %>% mutate(x2 = interaction(phospho, buried))
p <- ggplot(pt_signif, aes(x=x2, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c('#00AA00','#D7F4D7'))
p <- p+xlab('')+ylab(expression(Y[fungi] - Y[metazoa] ~  (pi[Pelican])))
p <- p+theme(axis.text=element_text(size=11.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(comparisons = list(c('non_pY.buried','pY.buried'),
                                        c('non_pY.intermediate','pY.intermediate'),
                                        c('non_pY.exposed','pY.exposed')),test='ks.test',test.args=list(alternative = "two.sided"))


```

# As before but this time for FPLV+3

```{r}

pel_tab_flank <- pel_tab[,7]
Pp3 <- substr(pel_tab_flank,11,11)
FPILVp3_dex <- which(Pp3 %in% c('F','P','I','L','V'))

pel_tab_FPILVp3 <- pel_tab[FPILVp3_dex,]

######

# Extract the parameters for each -3 D/E residue (where possible)

```


# Extract the parameter values where possible

```{r}

pelican_results <- list.files('/home/david/Documents/Work/HFSP_pelican/pelican_results')

count = 0

missing_vec <- NULL

selec_df <- NULL

for (i in 1:nrow(pel_tab_FPILVp3)) {
  
  print(i)
  
  accession <- pel_tab_FPILVp3[i,1]
  pos <- pel_tab_FPILVp3[i,4]
  
  #E/D-3
  
  pos <- pos+3
  
  rsa <- pel_tab_FPILVp3[i,2]
  disorder <- pel_tab_FPILVp3[i,3]
  
  # Retrieve the Pelican results for this protein
  
  pel_res_dex <- which(pelican_results %in% accession)
  
  # Skip if we do not have any Pelican results for this protein
  
  if (length(pel_res_dex) == 0) {next}
  
  # Skip if we have results (apparently?) but no parameters).
  
  param_tab <- paste('/home/david/Documents/Work/HFSP_pelican/pelican_results_parameters/',accession,'_pelican_parameters.txt',sep='')
  
  if(length(param_tab) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  param_lines <- readLines(param_tab)
  
  if(length(param_lines) == 0) {count=count+1; missing_vec <- c(missing_vec,accession); next}
  
  params <- read.table(param_tab, head=T)
  
  # Map the phosho position to the alignment position
  
  map_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/mapping_tables/',paste(accession,'_mapping.txt',sep=''),sep=''), head=T)
  
  al_pos <- map_tab[map_tab[,2] == pos,3]
  trim_pos <- map_tab[map_tab[,2] == pos,4]
  
  # If we cannot locate a mapped position, then this means that the position was gappy and trimmed out by trimAL
  
  if (length(trim_pos) == 0) {next}
  
  # Alignment numbering is Python-based and so we need to account for that
  
  pel_pos <- trim_pos-1 
  
  phos_params <- params[params[,2] == pel_pos,]
  phos_params_0 <- phos_params[which(phos_params[,7] == '0'),]
  phos_params_1 <- phos_params[which(phos_params[,7] == '1'),]
  
  # Compile parameters (simply sum frequencies from all relevant residues)
  
  phos_params_0_Y <- phos_params_0[,colnames(phos_params_0) %in% c('F','P','I','L','V')]
  phos_params_1_Y <- phos_params_1[,colnames(phos_params_1) %in% c('F','P','I','L','V')]  
  phos_params_0_Y <- sum(phos_params_0_Y)
  phos_params_1_Y <- sum(phos_params_1_Y)
  
  # aaqtr pvalue
  
  pval_tab <- read.table(paste('/home/david/Documents/Work/HFSP_pelican/pelican_results/',accession,'/',accession,'_results/','all_sites.tsv',sep=''), head=T)
  pval_tab <- pval_tab[pval_tab[,2] == pel_pos,]
  naa <-  pval_tab[,4]
  multi_pval <- pval_tab[,5]
  aaqtr_pval <- pval_tab[,6]    
  
  # pY or non-pY
  
  class <- pel_tab_FPILVp3[i,12]
  
  # Put it all together
  
  selec_vec <- c(accession,rsa,disorder,pos,al_pos,trim_pos,phos_params_0_Y,phos_params_1_Y,naa,multi_pval,aaqtr_pval, class)
  
  selec_df <- rbind(selec_df, selec_vec)
  
} 

colnames(selec_df) <- c('accession', 'RSA','disorder','pos','al_pos', 'trim_pos', '0_FPILV','1_FPILV', 'naa','multinomial_p','aaqtr_p', 'class')
rownames(selec_df) <- NULL

selec_df_FPILVp3 <- selec_df

```

# Do FDR/BH-adjustment on the p-values and export table

```{r}

bh_adjust <- p.adjust(as.numeric(selec_df_FPILVp3[,11]),method='BH') #FDR and BH are exactly the same
selec_df_FPILVp3 <- data.frame(selec_df_FPILVp3,bh_adjust)
selec_df_FPILVp3 <- selec_df_FPILVp3[c(1:11,13,12)]

colnames(selec_df_FPILVp3) <- c('accession','RSA','order','sequence','alignment','trimmed','fungi_pelican_DE','metazoa_pelican_DE','naa','multinomial_p','pelican_pvalue','pelican_padjust', 'class')

selec_df_FPILVp3 <- selec_df_FPILVp3[,-c(9,10)]

# Difference between metazoa and fungal parameters

diff_vec <- as.numeric(selec_df_FPILVp3[,7]) - as.numeric(selec_df_FPILVp3[,8])

selec_df_FPILVp3 <- data.frame(selec_df_FPILVp3[,1:8],diff_vec,selec_df_FPILVp3[,9:11])
colnames(selec_df_FPILVp3)[9] <- 'pelican_param_Y_fungi_Y_metazoa' 

```

# Violin plot (P/I/L/V+3, Pelican parameters, FDR < 0.05)

```{r}

pt_all <- selec_df_FPILVp3[,c(2,9,11,12)]
colnames(pt_all) <- c('RSA','param','signif','class')
pt_all <- data.frame(pt_all,0)
pt_all[pt_all[,1] < 0.2,5] <- 'buried'
pt_all[pt_all[,1] > 0.4,5] <- 'exposed'
pt_all[pt_all[,1] >= 0.2 & pt_all[,1] <= 0.4,5] <- 'intermediate'

### 0.05

pt_signif <- pt_all[pt_all[,3] < 0.05,]
colnames(pt_signif) <- c('RSA','param','signif','phospho','buried')

###

sample_sizes <- table(paste(pt_signif[,4],pt_signif[,5]))
sample_sizes <- sample_sizes[c(1,4,3,6,2,5)]

###

## We will use ggsignif to plot the significance values. However, ggsignif does not seem to work very well when the data is grouped.
## Therefore, far below I have constructed a df that allows me to implement ggsignif to calculate the p-values. Then, I will
# take these p-values and then manually add them to my distributions below.

pt_signif$buried <- factor(pt_signif$buried, levels = c('buried','intermediate','exposed'))

####

median.quartile <- function(x){
  out <- quantile(x, probs = c(0.25,0.5,0.75))
  names(out) <- c("ymin","y","ymax")
  return(out) 
}

mycol <- viridis::rocket(30)

####

library(ggsignif)

p <- ggplot(pt_signif, aes(x=buried, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p <- p+scale_fill_manual(values=c('#FFCC00','#FFEEAA'))
p <- p+xlab('')+ylab(expression(ED[fungi] - ED[metazoa] ~  (pi[Pelican])))+ggtitle('F/P/I/L/V+3')
p <- p+theme(plot.title = element_text(hjust = 0.5))
p <- p+theme(axis.text=element_text(size=10.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=12.2,face="plain"),plot.title=element_text(size=12.5,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(y_position = c(1.08,1.08,1.08), xmin = c(0.8,1.8,2.8), 
              xmax = c(1.2,2.2,3.2), annotation = c("0.86","0.15","0.54"),
              tip_length = 0.02)
p <- p+theme(legend.position = 'none')
p <- p + geom_text(data=data.frame(), aes(x=c(0.78,1.22,1.78,2.22,2.78,3.22), y=rep(1.23,6), label=sample_sizes), size=2.85, inherit.aes = F)

ggsave(file='Supplementary_figure_10c_FPILV.pdf', plot=p, width=4.25, height=3.15)


### geom_signif significance

pt_signif <- pt_signif %>% mutate(x2 = interaction(phospho, buried))
p <- ggplot(pt_signif, aes(x=x2, y=param, fill=phospho)) + geom_violin(color='black', lwd=1.03, width=0.85, position = position_dodge(width = 0.815))
p <- p+theme_bw()
p <- p + theme(panel.border= element_blank())
p <- p + stat_summary(fun.data = median.quartile, color = colors()[180], lwd=0.90, position = position_dodge(width = 0.80))
p <- p+scale_fill_manual(values=c(mycol[30],mycol[12]))
p <- p+xlab('')+ylab(expression(Y[fungi] - Y[metazoa] ~  (pi[Pelican])))
p <- p+theme(axis.text=element_text(size=11.5),axis.title.x=element_text(size=11.5,face="plain"),axis.title.y=element_text(size=15.2,face="plain"),plot.title=element_text(size=12,face='bold'))
p <- p+guides(fill=guide_legend(""))
p <- p + theme(axis.ticks.x = element_line(color = c(NA, NA, NA)))
p <- p+theme(legend.margin=margin(0,0,0,0),legend.box.margin=margin(-10,-2,-10,-10))
p <- p + geom_signif(comparisons = list(c('non_pY.buried','pY.buried'),
                                        c('non_pY.intermediate','pY.intermediate'),
                                        c('non_pY.exposed','pY.exposed')),test='ks.test',test.args=list(alternative = "two.sided"))


```

# Supplementary figure 10d

```{r}

# Filter for significant sites

pel_tab_signif <- pel_tab[pel_tab[,11] < 0.05,]

# Parameter distribution for all significant sites

quantile(pel_tab_signif[,9],probs=seq(0,1,0.01)) #0.8 seems to mark the 95% percentile mark

# Significant pY

pel_tab_signif_pY <- pel_tab_signif[pel_tab_signif[,12] == 'pY',]

# Retrieve the top-ranked counter-selected residues

# strongly counter-selected sites 
pel_tab_top_rank <- pel_tab_signif_pY[which(pel_tab_signif_pY[,9] > 0.5),] # pi_Fungi - pi_Metazoa is greater than 0.5
pel_tab_top_rank_flank_05 <- pel_tab_top_rank[,7]

# weakly counter-selected sites 
pel_tab_top_rank <- pel_tab_signif_pY[which(pel_tab_signif_pY[,9] > 0.0 & pel_tab_signif_pY[,9] < 0.25),] # pi_Fungi - pi_Metazoa is greater than 0 but less than 0.25
pel_tab_top_rank_flank_01 <- pel_tab_top_rank[,7]

# -3

n3_05_tab <- table(substr(pel_tab_top_rank_flank_05,5,5))/sum(table(substr(pel_tab_top_rank_flank_05,5,5))) 
n3_01_tab <- table(substr(pel_tab_top_rank_flank_01,5,5))/sum(table(substr(pel_tab_top_rank_flank_01,5,5)))

DE_n3_05 <- sum(n3_05_tab[names(n3_05_tab) %in% c('D','E')])
DE_n3_01 <- sum(n3_01_tab[names(n3_01_tab) %in% c('D','E')])

# -1

n1_05_tab <- table(substr(pel_tab_top_rank_flank_05,7,7))/sum(table(substr(pel_tab_top_rank_flank_05,7,7))) 
n1_01_tab <- table(substr(pel_tab_top_rank_flank_01,7,7))/sum(table(substr(pel_tab_top_rank_flank_01,7,7)))

ILV_n1_05 <- sum(n1_05_tab[names(n1_05_tab) %in% c('I','L','V')])
ILV_n1_01 <- sum(n1_01_tab[names(n1_01_tab) %in% c('I','L','V')])

# +3

p3_05_tab <- table(substr(pel_tab_top_rank_flank_05,11,11))/sum(table(substr(pel_tab_top_rank_flank_05,11,11))) 
p3_01_tab <- table(substr(pel_tab_top_rank_flank_01,11,11))/sum(table(substr(pel_tab_top_rank_flank_01,11,11)))

FPILV_p3_05 <- sum(p3_05_tab[names(p3_05_tab) %in% c('F','P','I','L','V')])
FPILV_p3_01 <- sum(p3_01_tab[names(p3_01_tab) %in% c('F','P','I','L','V')])

# Conclusion: no difference in motifs when comparing between strongly and weakly counter-selected Y sites

```

# Make GGplots of the data

```{r}

library(ggplot2)

col1 <- c('D/E-3','I/L/V-1','F/P/I/L/V+3')
col2 <- c(DE_n3_01,ILV_n1_01,FPILV_p3_01)*100
col3 <- c('0.0 < x < 0.25','0.0 < x < 0.25','0.0 < x < 0.25')

df1 <- data.frame(col1,col2,col3)

col1 <- c('D/E-3','I/L/V-1','F/P/I/L/V+3')
col2 <- c(DE_n3_05,ILV_n1_05,FPILV_p3_05)*100
col3 <- c('x > 0.5', 'x > 0.5', 'x > 0.5')
df2 <- data.frame(col1,col2,col3)

df <- rbind(df1,df2)

df$col1 <- factor(df$col1, levels = c('D/E-3','I/L/V-1','F/P/I/L/V+3'))

##

p <- ggplot(df, aes(x=col1,y=col2,fill=col1))+geom_bar(stat='identity', width=0.5)
p <- p+theme_bw()
p <- p + facet_wrap(vars(col3))
p <- p+ coord_cartesian(ylim = c(0, 50))
p <- p+xlab('')+ylab('% frequency')
p <- p+theme(legend.position="none")
p <- p+scale_fill_manual(values=c(mycol[12],'#00AA00','#FFCC00'))

ggsave(file='/home/david/Documents/Work/Bradley_et_al_2023/Counter_selection_figure/github_files/Supplementary_figure_10d.pdf', plot=p, width=4.6, height=2.6)

```
