---
title: "Figure_4c"
author: "David Bradley"
date: '2023-07-17'
output: html_document
---

# For each of the human kinases with a (relatively) strong phosphorylation signal, retrieve the KSRs from the Bachman paper
# and then check to see if they are orthologues or not of the sc proteins that are phosphorylated by that kinase

# We will start by using the Src kinase as an example

```{r}

# Retrieve the kinase-substrate relationship (KSR) data from ProtMapper (Bachman et al., 2022, bioRxiv)

KSRs <- read.csv('export.csv')

# filter for KSRs that have a 'belief' score (i.e. confidence score) greater than 0.75 (quite a conservative threshold)

KSRs <- KSRs[KSRs[,11] > 0.75,]

# We will use Src as our initial example

SRC_KSRs <- KSRs[which(KSRs[,4] == 'SRC'),]
SRC_substrate_ids_uniprot <- unique(SRC_KSRs[,6])
SRC_substrate_ids_uniprot <- rapply(strsplit(SRC_substrate_ids_uniprot,split='-'), function(x) x[1]) #Remove isoform info (cannot be mapped to Ensembl)

# Map to Ensembl using 'bitr' function from ClusterProfiler

library(clusterProfiler)
library(org.Hs.eg.db)
uniprot_ensembl <- bitr(SRC_substrate_ids_uniprot, fromType="UNIPROT", toType=c("ENSEMBL"), OrgDb="org.Hs.eg.db")
SRC_substrate_ids_ensembl <- uniprot_ensembl[,2]

# Extract all of the unique Src substrates in yeast

SRC_master <- read.csv(paste('pY-SRC_master.csv',sep='')) # Locat the 'master' file for SRC kinase
SRC_yeast_pY_ensembl <- unique(SRC_master$ensembl_IDs) # Extract Ensembl IDs
SRC_yeast_pY_ensembl <- SRC_yeast_pY_ensembl #ensemble(SRC_yeast_pY_ensembl,1,7)
SRC_yeast_pY_ensembl <- SRC_yeast_pY_ensembl[!is.na(SRC_yeast_pY_ensembl)]

# Cross reference this with the orthology table for phosphorylated proteins

sc_hs_df_phospho <- read.table('sc_hs_df_phospho_relaxed.txt') # NB this 'relaxed' table includes proteins that may be native pY because they were detected once as a native pY

# subset the orthology table only for the substrates of Src

sc_hs_df_phospho_sc_SRC <- sc_hs_df_phospho[sc_hs_df_phospho[,1] %in% SRC_yeast_pY_ensembl,]

# subset further for only those phosphorylated substrates that have human orthologues that are also phosphorylated by SRC
# i.e. number of cases where both yeast and human proteins are known to be phosphrylated by Src

sc_hs_df_phospho_sc_SRC_hs_SRC <- sc_hs_df_phospho_sc_SRC[sc_hs_df_phospho_sc_SRC[,2] %in% SRC_substrate_ids_ensembl,]

# calculate fractions

# Number of yeast Src susbstrates that have at least one human orthologue that is phosphorylated by SRC
SRC_sc_over_hs <- length(unique(sc_hs_df_phospho_sc_SRC_hs_SRC[,1]))/length(unique(SRC_yeast_pY_ensembl)) 

# Number of human_substrates that have at least one yeast ortholog that is spuriously phosphorylated
SRC_hs_over_sc <- length(unique(sc_hs_df_phospho_sc_SRC_hs_SRC[,2]))/length(unique(SRC_substrate_ids_ensembl)) 

```

# Iterate across all human kinases with appreciable specificity (we cannot do this for vSRC for obvious reasons)

```{r}

master_files <- list.files('') # Path to the directory containing all of the master files for each kinase
active_kinases <- c('ABL1','ABL2','FYN','EPHB4','EPHA3','LCK','LYN','SRC','EPHB1','EPHB3','FGFR2','MERTK','ABL1','FRK','FYN','LCK','LYN','SRC','EPHB1','EPHB3','FGFR2','MERTK')

# Only 5 of the kinases have a non-negligible sample-size of known substrates in ProtMapper:
active_kinases <- c('ABL1','FYN','LCK','LYN','SRC')

# orthology table for all pY-phosphorylated yeast proteins detected in this study

sc_hs_df_phospho <- read.table('sc_hs_df_phospho_relaxed.txt') # NB this 'relaxed' table includes proteins that may be native pY because they were detected once as a native pY

sc_frac_vec <- NULL # conserved KSRs as a fraction of total substrates in yeast
hs_frac_vec <- NULL # conserved KSRs as a fraction of total substrates in human
hs_ortho_num_vec <- NULL # number of known substrates in human (i.e. the sample size)

for (i in 1:length(active_kinases)) {
  
    active_kinase <- active_kinases[i]
    
    grep_tag <- paste('-',active_kinase,'_',sep='') 
    
    SRC_KSRs <- KSRs[which(KSRs[,4] == active_kinase),] #N.B. the code refers to 'SRC' but the data in fact corresponds to whatever is the 'active kinase' for this iteration of the for loop.
    
    if(nrow(SRC_KSRs) == 0) {stop('no kinase KSRs?')}
    
    SRC_substrate_ids_uniprot <- unique(SRC_KSRs[,6])
    SRC_substrate_ids_uniprot <- rapply(strsplit(SRC_substrate_ids_uniprot,split='-'), function(x) x[1]) # Remove isoform info (cannot be mapped to Ensembl)
    
    # Map to Ensembl
    
    library(clusterProfiler)
    library(org.Hs.eg.db)
    uniprot_ensembl <- bitr(SRC_substrate_ids_uniprot, fromType="UNIPROT", toType=c("ENSEMBL"), OrgDb="org.Hs.eg.db")
    SRC_substrate_ids_ensembl <- uniprot_ensembl[,2]
    
    # Count the number of known human substrates
    hs_ortho_num_vec <- c(hs_ortho_num_vec,length(SRC_substrate_ids_ensembl))
    
    # Extract all of the unique substrates for the kinase
    
    grep_dex <- grep(grep_tag,master_files) # index of the master file corresponding to the kinase of interest, found by grepping the kinase name against the list of master files 
    
    if(length(grep_dex) != 1) {stop('Cannot find the master file')}
    
    # Read in the master file corresponding to the active kinase in question
    SRC_master <- read.csv(paste(master_files[grep_dex],sep=''))
    SRC_yeast_pY_ensembl <- unique(SRC_master[,7])
    SRC_yeast_pY_ensembl <- SRC_yeast_pY_ensembl #substr(SRC_yeast_pY_ensembl,1,7)
    SRC_yeast_pY_ensembl <- SRC_yeast_pY_ensembl[!is.na(SRC_yeast_pY_ensembl)]
    
    # subset the orthology table only for the substrates of the active kinase in question
    
    sc_hs_df_phospho_sc_SRC <- sc_hs_df_phospho[sc_hs_df_phospho[,1] %in% SRC_yeast_pY_ensembl,]
    
    # subset further for only those phosphorylated substrates that have human orthologues that are also phosphorylated by SRC
    # i.e. number of cases where both yeast and human proteins are known to be phosphrylated by Src
    
    sc_hs_df_phospho_sc_SRC_hs_SRC <- sc_hs_df_phospho_sc_SRC[sc_hs_df_phospho_sc_SRC[,2] %in% SRC_substrate_ids_ensembl,]
    
    # calculate fractions
    
    # Number of yeast Src susbstrates that have at least one human orthologue that is phosphorylated by SRC
    SRC_sc_over_hs <- length(unique(sc_hs_df_phospho_sc_SRC_hs_SRC[,1]))/length(unique(SRC_yeast_pY_ensembl)) 
    
    # Number of human_substrates that have at least one yeast ortholog that is spuriously phosphorylated
    SRC_hs_over_sc <- length(unique(sc_hs_df_phospho_sc_SRC_hs_SRC[,2]))/length(unique(SRC_substrate_ids_ensembl)) 
      
    # append fractions to the vector
    
    sc_frac_vec <- c(sc_frac_vec,SRC_sc_over_hs)
    hs_frac_vec <- c(hs_frac_vec,SRC_hs_over_sc)
    
}

names(sc_frac_vec) <- active_kinases
names(hs_frac_vec) <- active_kinases
names(hs_ortho_num_vec) <- active_kinases

```

# Generate a heatmap of the data using ComplexHeatmaps

```{r}

library(ComplexHeatmap)
library('RColorBrewer')
library(circlize)
library(viridis)


# conserved KSRs as a fraction of total substrates in yeast

pdf(file = "KSR_yeast.pdf",   # The directory you want to save the file in
    width = 5, # The width of the plot in inches
    height = 1.5) 

Heatmap(t(sc_frac_vec),cluster_columns=F,cluster_rows=F,col=colorRamp2(c(0, 0.25), c('white',colors()[499])), 
        row_names_side='left',
       # heatmap_width=0.5,
        width=unit(8,'cm'),
       # heatmap_height=2,
        height=unit(0.7,'cm'),
        border=TRUE,
        row_title='',
        row_title_gp=gpar(fontsize = 13),
        row_names_rot=0,
        row_names_centered=TRUE,
        row_names_gp=gpar(fontsize = 6.0),
        
     #   Cells with no data are colored in white
            cell_fun = function(j, i, x, y, w, h, col) { # add text to each grid
              grid.text(round(sc_frac_vec[j]*100,2), x, y,gp=gpar(fontsize = 6.0, col='black'))},
            
        show_column_names=TRUE,
        #bottom_annotation = HeatmapAnnotation(
        #text = anno_text(colnames(top_ptm_df), rot = 0, offset = unit(0.75, "npc"), just = "right"),
        #annotation_height = max_text_width(colnames(top_ptm_df))),
        column_title='',
        column_title_side='bottom',
        column_title_gp=gpar(fontsize = 13),
        column_names_gp=gpar(fontsize=7.0),
        #col_names_rot=90,
        rect_gp=(gpar(lwd=0.9, fontfamily='mono')), 
       
   heatmap_legend_param = list(
    at = c(0.0,0.25),
    labels = c("0", "25"),
    title = "Sc-pY \n % conservation",
    legend_height = unit(1.15, "cm"),
    legend_width = unit(1, "cm"),
    border='black',
    lwd=1.7,
    title_position = "leftcenter-rot",
    title_gp = gpar(fontsize = 5.5, fontface='bold')
))

dev.off()

# save (3.00 x 8.00; landscape)

# conserved KSRs as a fraction of total substrates in human

# Here is the annotation for the total number of substrates

pdf(file = "KSR_human.pdf",   # The directory you want to save the file in
    width = 5, # The width of the plot in inches
    height = 1.5) 

ha1 = HeatmapAnnotation(
    dist1 = anno_barplot(hs_ortho_num_vec
        , 
        bar_width = 1, 
        gp = gpar(col = "white", fill = "black"), 
        border = FALSE,
        gap = unit(1, "points"),
        axis=TRUE,
        height = unit(2, "cm")
    ), show_annotation_name = FALSE)

Heatmap(t(hs_frac_vec),cluster_columns=F,cluster_rows=F,col=colorRamp2(c(0, 0.25), c('white',colors()[617])), 
        row_names_side='left',
       # heatmap_width=0.5,
        width=unit(8,'cm'),
       # heatmap_height=2,
        height=unit(0.7,'cm'),
        border=TRUE,
        row_title='',
        row_title_gp=gpar(fontsize = 13),
        row_names_rot=0,
        row_names_centered=TRUE,
        row_names_gp=gpar(fontsize = 6.0),
        
        # Cells with no data are colored in white
            cell_fun = function(j, i, x, y, w, h, col) { # add text to each grid
              grid.text(round(hs_frac_vec[j]*100,2), x, y,gp=gpar(fontsize = 6.0, col='black'))},
            
        show_column_names=TRUE,
        #bottom_annotation = HeatmapAnnotation(
        #text = anno_text(colnames(top_ptm_df), rot = 0, offset = unit(0.75, "npc"), just = "right"),
        #annotation_height = max_text_width(colnames(top_ptm_df))),
        column_title='',
        column_title_side='bottom',
        column_title_gp=gpar(fontsize = 13),
        column_names_gp=gpar(fontsize=7.0),
        #col_names_rot=90,
        rect_gp=(gpar(lwd=0.9, fontfamily='mono')), 
    top_annotation = ha1,   
  heatmap_legend_param = list(
    at = c(0.0,0.25),
    labels = c("0", "25"),
    title = "Hs-pY \n % conservation",
    legend_height = unit(1.15, "cm"),
    legend_width = unit(1, "cm"),
    border='black',
    lwd=1.7,
    title_position = "leftcenter-rot",
    title_gp = gpar(fontsize = 6.5, fontface='bold')
))

dev.off()

# save (3.00 x 8.00; landscape)

```

